A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
Enshrinken

%\newcommand{\examplexG}[5] {
%    \begin{minipage}{.2\textwidth}
%    \tikz {
%        \graph [nodes={draw, circle, minimum width=.6cm}, circular placement, radius=1cm,
%                clockwise=5] {
%                    1[label=90:#1],2[label=0:#2],3[label=0:#3],4[label=180:#4],5[label=180:#5];
%            1--4; 1--5; 2--3; 2--5; 3--5;
%        };
%    }
%    \end{minipage}
%}
%\newcommand{\examplexH}[6] {
%    \begin{minipage}{.2\textwidth}
%    \tikz {
%        \graph [nodes={draw, circle, minimum width=.6cm}, circular placement, radius=1.1cm,
%                clockwise=6, phase=60] {
%                    a[label=0:#1],b[label=0:#2],c[label=0:#3],d[label=180:#4],e[label=180:#5],f[label=180:#6];
%            a--b; a--c; a--e; b--d; b--f; c--d; c--e; c--f; d--f; e--f;
%        };
%    }
%    \end{minipage}
%}

@@

\begin{figure}[t]
\centering
    \includegraphics{graph_G}
    \includegraphics{graph_H}
%    \examplexG{}{}{}{}{}
%    \examplexH{}{}{}{}{}{}
\caption{Example graphs $G$ and $H$.}
\label{fig:alg1}
\end{figure}

>>>>

\newcommand{\examplexG}[5] {
    \begin{minipage}{.2\textwidth}
    \tikz {
        \graph [nodes={draw, circle, minimum width=.5cm, inner sep=1pt}, circular placement, radius=0.8cm,
                clockwise=5] {
                    1[label=90:#1],2[label=0:#2],3[label=0:#3],4[label=180:#4],5[label=180:#5];
            1--4; 1--5; 2--3; 2--5; 3--5;
        };
    }
    \end{minipage}
}
\newcommand{\examplexH}[6] {
    \begin{minipage}{.2\textwidth}
    \tikz {
        \graph [nodes={draw, circle, minimum width=.5cm, inner sep=1pt}, circular placement, radius=0.8cm,
                clockwise=6, phase=60] {
                    a[label=0:#1],b[label=0:#2],c[label=0:#3],d[label=180:#4],e[label=180:#5],f[label=180:#6];
            a--b; a--c; a--e; b--d; b--f; c--d; c--e; c--f; d--f; e--f;
        };
    }
    \end{minipage}
}

@@

\begin{figure}[t]
\centering
    \examplexG{}{}{}{}{}
    \examplexH{}{}{}{}{}{}
\caption{Example graphs $G$ and $H$.}
\label{fig:alg1}
\end{figure}
